\subsection{\msrcode{actAdministrator} Actor}


\begin{actortable}
	\addheading{Actor}
	
	\adddoublerow{actAdministrator}{PI variant: The actor Administrator is in charge of treating requested points of interests and 
				adding, updating or deleting points of interests. The Administrator receives a request to add a 
				new PI from a Person which the actor Coordinator checks before delivering them to the actor 
				Administrator.
				Access Rights variant: The actor Administrator is in charge of managing coordinators. This includes creating
				and deleting them and updating their access rights.}
	
	\addrowheading{Extends}
	\addsinglerow{lu.uni.lassy.excalibur.MyCrash.G02.environment.actAuthenticated}
	
	
	
	

	\addrowheading{OutputInterfaces}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeGetAllRequestsFromCoordinator}
			{\msrcode{oeGetAllRequestsFromCoordinator():ptBoolean}}}
			{The output event oeGetAllRequestsFromCoordinator retrieves a list of requests which the actor Coordinator checked.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeTreatRequest}
			{\msrcode{oeTreatRequest(ARequestID:dtID):ptBoolean}}}
			{The output event oeTreatRequest modifies the request status to treated.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeSolveRequest}
			{\msrcode{oeSolveRequest(ARequestID:dtID):ptBoolean}}}
			{The output event oeTreatRequest modifies the request status to solved.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeAddPI}
			{\msrcode{oeAddPI(APIID:dtID, APIName:dtName, APICity:dtCity, APIGPSLocation:dtGPSLocation, APIDescription:dtDescription, APICategory:etCategory):ptBoolean}}}
			{The output event oeAddPI adds a new point of interest requested by the actor Person.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeUpdatePI}
			{\msrcode{oeUpdatePI(APIID:dtID, APIName:dtName, APICity:dtCity, APIGPSLocation:dtGPSLocation, APIDescription:dtDescription, APICategory:etCategory):ptBoolean}}}
			{The output event oeUpdatePI updates a point of interest.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeDeletePI}
			{\msrcode{oeDeletePI(APIID:dtID):ptBoolean}}}
			{The output event oeDeletePI deletes a point of interest.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeAddCoordinator}
			{\msrcode{oeAddCoordinator(AdtCoordinatorID:dtCoordinatorID, AdtLogin:dtLogin, AdtPassword:dtPassword, CoordinatorAccessRights:etCrisisType):ptBoolean}}}
			{The output event oeAddCoordinator creates a new coordinator in the system.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeDeleteCoordinator}
			{\msrcode{oeDeleteCoordinator(AdtCoordinatorID:dtCoordinatorID):ptBoolean}}}
			{The output event oeDeleteCoordinator deletes a coordinator in the system.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeUpdateCoordinatorAccessRights}
			{\msrcode{oeUpdateCoordinatorAccessRights(AdtCoordinatorID:dtCoordinatorID, CoordinatorAccessRights:etCrisisType):ptBoolean}}}
			{The output event oeUpdateCoordinatorAccessRights updates a coordinator's access rights in the system.}
	
	\addrowheading{InputInterfaces}
	\addnumbereddoublerow{IN}{\msrcode{ieRequestList():ptBoolean}}
							 {The input event ieRequestList returns a list of checked requests from the actor Coordinator 
							 to the actor Administrator.}
	\addnumbereddoublerow{IN}{\msrcode{ieRequestBeingTreated():ptBoolean}}
							 {The input event ieRequestBeingTreated specifies that the request is being treated.}
	\addnumbereddoublerow{IN}{\msrcode{ieRequestSolved():ptBoolean}}
							 {The input event ieRequestSolved confirms that the request was solved.}
	\addnumbereddoublerow{IN}{\msrcode{iePIAdded():ptBoolean}}
							 {The input event iePIAdded confirms that the requested point of interest has been added.}
	\addnumbereddoublerow{IN}{\msrcode{iePIUpToDate():ptBoolean}}
							 {The input event iePIUpToDate confirms that the requested point of interest has been updated.}
	\addnumbereddoublerow{IN}{\msrcode{iePIDeleted():ptBoolean}}
							 {The input event iePIDeleted confirms that the requested point of interest has been deleted.}
	\addnumbereddoublerow{IN}{\msrcode{ieCoordinatorAdded():ptBoolean}}
							 {The input event ieCoordinatorAdded confirms if a coordinator was successfully added to the system.}
	\addnumbereddoublerow{IN}{\msrcode{ieCoordinatorDeleted():ptBoolean}}
							 {The input event ieCoordinatorDeleted confirms if a coordinator was successfully deleted in the system.}
	\addnumbereddoublerow{IN}{\msrcode{ieCoordinatorUpdated():ptBoolean}}
							 {The input event ieCoordinatorUpdated confirms if a coordinator's access rights were successfully updated in the system.}
	
\end{actortable}
