\subsection{\msrcode{actCoordinator} Actor}


\begin{actortable}
	\addheading{Actor}
	
	\adddoublerow{actCoordinator}{PI variant: The actor Coordinator is in charge of checking the requested points of
				 interest of their existence in the system and to deliver the non-existing requested
				 points of interest to the actor Administrator.
				 Access Rights variant: The actor Coordinator is in charge of managing and monitoring alerts and crisis.
				 This means he has the overview of over all alerts and crisis. He decides weather a alert should be validated
				 or not. All the crisis managed by him, which means he is the only actor interacting and handling crisis.}
	
	\addrowheading{Extends}
	\addsinglerow{lu.uni.lassy.excalibur.MyCrash.G02.environment.actAuthenticated}
	
	
	
	

	\addrowheading{OutputInterfaces}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeGetAllRequests}
			{\msrcode{oeGetAllRequests():ptBoolean}}}
			{The output event oeGetAllRequests retrieves a list of requests sent by the actor Person.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeCheckAvailability}
			{\msrcode{oeCheckAvailability(ARequestName:dtName, ARequestCity:dtCity, ARequestCategory:etCategory):ptBoolean}}}
			{The output event oeCheckAvailability confirms that a requested point of interest sent by the actor 
			Person exists already in the system or not and sets the request ignored attribute to the 
			corresponding value.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeDeliverRequest}
			{\msrcode{oeDeliverRequest(ARequestID:dtID):ptBoolean}}}
			{The output event oeDeliverRequest sends a checked request sent by the actor Person to the actor Administrator.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeInvalidateAlert}
			{\msrcode{oeInvalidateAlert(AdtAlertID:dtAlertID):ptBoolean}}}
			{The output event oeInvalidateAlert puts the status of an alert to invalid.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeValidateAlert}
			{\msrcode{oeValidateAlert(AdtAlertID:dtAlertID):ptBoolean}}}
			{The output event oeValidateAlert puts the status of an alert to valid.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeGetAlertSet}
			{\msrcode{oeGetAlertSet(AetAlertStatus:etAlertStatus):ptBoolean}}}
			{The output event oeGetAlertSet requests a list with every existing alert in the system matching the given parameters.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeCloseCrisis}
			{\msrcode{oeCloseCrisis(AdtCrisisID:dtCrisisID):ptBoolean}}}
			{The output event oeCloseCrisis puts the status of a crisis to closed.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeGetCrisisSet}
			{\msrcode{oeGetCrisisSet(AetCrisisStatus:etCrisisStatus):ptBoolean}}}
			{The output event oeGetCrisisSet requests a list with every existing crisis in the system matching the given parameters.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeSetCrisisHandler}
			{\msrcode{oeSetCrisisHandler(AdtCrisisID:dtCrisisID):ptBoolean}}}
			{The output event oeSetCrisisHandler sets a coordinator as handler of a crisis.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeReportOnCrisis}
			{\msrcode{oeReportOnCrisis(AdtCrisisID:dtCrisisID, AdtComment:dtComment):ptBoolean}}}
			{The output event oeReportOnCrisis adds a report to a crisis.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeSetCrisisStatus}
			{\msrcode{oeSetCrisisStatus(AdtCrisisID:dtCrisisID, AetCrisisStatus:etCrisisStatus):ptBoolean}}}
			{The output event oeSetCrisisStatus changes the status of a crisis.}
	\addnumbereddoublerow{OUT}{\hypertarget{actCoordinator.outactCoordinator.oeSetCrisisType}
			{\msrcode{oeSetCrisisType(AdtCrisisID:dtCrisisID, AetCrisisType:etCrisisType):ptBoolean}}}
			{The output event oeSetCrisisType changes the type of a crisis.}
	
	\addrowheading{InputInterfaces}
	\addnumbereddoublerow{IN}{\msrcode{ieRequestListToCheck():ptBoolean}}
							 {The input event ieRequestListToCheck returns a list of requests which have to be checked from the 
							 actor Person to the actor Coordinator.}
	\addnumbereddoublerow{IN}{\msrcode{ieRequestDelivered():ptBoolean}}
							 {The input event ieRequestDelivered specifies that the request has been delivered to the actor 
							 Coordinator.}
	\addnumbereddoublerow{IN}{\msrcode{ieCrisisSet():ptBoolean}}
							 {The input event ieCrisisSet returns a list with every existing crises in the system matching the given parameters.}
	\addnumbereddoublerow{IN}{\msrcode{ieAlertSet():ptBoolean}}
							 {The input event ieAlertSet returns a list with every existing alert in the system matching the given parameters.}
	
\end{actortable}
