\subsection{Primary types - Association types descriptions}




The table below is providing comments on the association types of the primary types.

\begin{associationtypes}
\addheading{Associations}
\adddoublerow{assctAdministratoractAdministrator}{frequent messages must be sent to coordinator especially in relation to coordinators they manage.}
\adddoublerow{assctAlertctCoordinator}{alerts need to be sent to coordinator in order to be validated or invalidated}
\adddoublerow{assctAlertctCrisis}{a crisis is related to one or more alerts as the alerts judged to concern all the same crisis due to their
location. An alert alerts exactly one crisis.}
\adddoublerow{assctAlertctPerson}{alerts are notified by person through the communication company. We need to keep an internal
representation of those person to allow for communication of alert handling.}
\adddoublerow{assctAuthenticatedactAuthenticated}{mainly used to determine if the login request of an authenticated actor can be granted based on the
given credentials and the registered ones.}
\adddoublerow{assctCoordinatoractCoordinator}{frequent messages must be sent to coordinator especially in relation to crisis they handle.}
\adddoublerow{assctCoordinatorctAdministrator}{one administrator manages more coordinators}
\adddoublerow{assctCrisisctCoordinator}{at any point in time we need to know if a coordinator is handling existing crisis or not.}
\adddoublerow{assctPersonactComCompany}{in order to communicate with person who informed about potential crisis, we need to record the
communication company to use to send them messages.}
\adddoublerow{assctPersonactPerson}{messages must be sent to person}
\adddoublerow{assctPIctAdministrator}{one administrator is charge of handling various point of interest}
\adddoublerow{assctPIctPerson}{several people can request several points of interests}
\adddoublerow{assctRequestctAdministrator}{one administrator is charge of handling various point of interest requests}
\adddoublerow{assctRequestctCoordinator}{several coordinators are charge of monitoring various point of interest requests}
\end{associationtypes}
