\subsection{Operation Model for oeSetCrisisHandler}

\label{OM-oeSetCrisisHandler}


The \msrcode{oeSetCrisisHandler} operation has the following properties:

	\begin{operationmodel}
	\addheading{Operation}
	\adddoublerow{oeSetCrisisHandler}{
	 sent to declare himself as been the handler of a crisis having the specified id.}

	\addrowheading{Parameters}
	\addnumbereddoublerow{}{AdtCrisisID: dtCrisisID}{the identification information used to determine the crisis} 

	\addrowheading{Return type}
	\addsinglerow{ptBoolean}

	\addrowheading{Pre-Condition (protocol)}
	\addnumberedsinglerow{PreP}{
	PreP 1 the system is started
	PreP 2 the actor logged previously and did not log out ! (i.e. the associated ctCoordinator instance
	is considered logged) }
		
	\addrowheading{Pre-Condition (functional)}
	\addnumberedsinglerow{PreF}{PreF 1 there exist one crisis having the given id in the pre-state. }

	\addrowheading{Post-Condition (functional)}
	\addnumberedsinglerow{PostF}{
	PostF 1 the ctCrisis instance having the provided id is in handled status at poststate and is associated
	to the actor that sends the message (which himself is notified with a textual message as
	confirmation).
	PostF 2 All the alerts related to this crisis are sent to the actor such that he can decide how to handle
	them.
	PostF 3 if the crisis was already handled at pre-sate then the associated handler actor is notified
	about the change of handler for one of his crisis (n.b. it might be the same even if not
	relevant).
	PostF 4 a message is sent to the communication company for any human related to an alert associated
	to the crisis. A human will receive as many messages as alerts he sent despite the fact that
	they might relate to the same crisis (i.e. one alert, one acknoledgement). }

	\addrowheading{Post-Condition (protocol)}
	\addnumberedsinglerow{PostP}{PostP 1 none }
	\end{operationmodel}



	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{OM-actCoordinator-oeSetCrisisHandler-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the operation.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the operation \emph{oeSetCrisisHandler}.},label=OM-actCoordinator-oeSetCrisisHandler-MCL-LST]

	/* Pre Protocol:*/ 
	preP{let TheSystem:ctState in
					let TheActor:actCoordinator in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = The Actor
					
					/* Pre P01 */
					TheSystem.vpStarted = true
					
					/* Pre P02 */
					TheActor.rnctAuthenticated.vpIsLogged = true}
	
	/* Pre Functional:*/
	preF{let TheSystem:ctState in
					let ColctCrisis:Bag(ctCrisis) in
				
					self.rnActor.rnSystem = TheSystem
				
					/* Pre F01 */
					TheSystem.rnctCrisis->select(id.eq(AdtCrisisID)) = ColctCrisis
					and ColctCrisis->size.eq(1)}
	
	/* Post Functional:*/ 
	postF{let TheSystem:ctState in
					let ThectCrisis:ctCrisis in
				
					self.rnActor.rnSystem = TheSystem
					
					/* Post F01 */
					TheSystem.rnctCrisis->select(id.eq(AdtCrisisID)) = ThectCrisis
					and ThectCrisis.AetCrisisStatus.eq("handled")
					and TheActor.rnInterfaceIN^ieMessage("Handler of the crisis " + AdtCrisisID + " is being handled by coordinator with id " + self.id)}
	
	/* Post Protocol:*/ 
	postP{ true}
	
	\end{lstlisting}
	\normalsize 
	
	
	
	





