\subsection{Operation Model for oeAddCoordinator}

\label{OM-oeAddCoordinator}


The \msrcode{oeAddCoordinator} operation has the following properties:

	\begin{operationmodel}
	\addheading{Operation}
	\adddoublerow{oeAddCoordinator}{
	 sent to add a new coordinator in the systems post state and environments post state.}

	\addrowheading{Parameters}
	\addnumbereddoublerow{}{AdtCoordinatorID: dtCoordinatorID}{used to initialize the id field} 
	\addnumbereddoublerow{}{AdtLogin: dtLogin}{used to initialize the login field} 
	\addnumbereddoublerow{}{AdtPassword: dtPassword}{used to initialize the password field} 
	\addnumbereddoublerow{}{CoordinatorAccessRights: etCrisisType}{used to initialize the access right field} 

	\addrowheading{Return type}
	\addsinglerow{ptBoolean}

	\addrowheading{Pre-Condition (protocol)}
	\addnumberedsinglerow{PreP}{PreP 1 the system is started}
	\addnumberedsinglerow{PreP}{PreP 2 the actor logged previously and did not log out ! (i.e. the associated ctAdministrator instance
	is considered logged) }
		
	\addrowheading{Pre-Condition (functional)}
	\addnumberedsinglerow{PreF}{PreF 1 it is supposed that there cannot exist a ctCoordinator instance with the same id attribute
	as the one the administrator wants to delete.}

	\addrowheading{Post-Condition (functional)}
	\addnumberedsinglerow{PostF}{
	PostF 1 the environment has a new instance of coordinator actor allowing for input/output message
	communication with the system.}
	\addnumberedsinglerow{PostF}{PostF 2 the systems state has a new instance of ctCoordinator initialized with the given values.}
	\addnumberedsinglerow{PostF}{PostF 3 the new actor instance and ctCoordinator instance are related.}
	\addnumberedsinglerow{PostF}{PostF 4 the new actor instance and ctCoordinator instance are related according to the authenticated
	association.}
	\addnumberedsinglerow{PostF}{PostF 5 the administrator actor is informed about the satisfaction of its request. }

	\addrowheading{Post-Condition (protocol)}
	\addnumberedsinglerow{PostP}{PostP 1 none}
	\end{operationmodel}



	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{OM-actAdministrator-oeAddCoordinator-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the operation.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the operation \emph{oeAddCoordinator}.},label=OM-actAdministrator-oeAddCoordinator-MCL-LST]

	/* Pre Protocol:*/ 
	preP{let TheSystem:ctState in
					let TheActor:actAdministrator in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = The Actor
					
					/* Pre P01 */
					TheSystem.vpStarted = true
					
					/* Pre P02 */
					TheActor.rnctAuthenticated.vpIsLogged = true}
	
	/* Pre Functional:*/
	preF{let TheSystem: ctState in
					let TheActor:actAdministrator in
					let ColctCoordinators:Bag(ctCoordinator) in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = TheActor
					
					/* PreF01 */
					and TheSystem.rnctCoordinator->select(id.eq(AdtCoordinatorID)) = ColctCoordinators
					and ColctCoordinators->isEmpty() = true}
	
	/* Post Functional:*/ 
	postF{let TheSystem: ctState in
					let TheactCoordinator:actCoordinator in
					let ThectCoordinator:ctCoordinator in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = TheActor
					
					/* PostF01 */
					TheactCoordinator.init()
					
					/* PostF02 */
					and ThectCoordinator.init(AdtCoordinatorID,AdtLogin,AdtPassword, CoordinatorAccessRights)
					
					/* PostF03 */
					and TheactCoordinator@post.rnctCoordinator = ThectCoordinator
					
					/* PostF04 */
					and ThectCoordinator@post.rnactAuthenticated = TheactCoordinator
					
					/* PostF05 */
					and TheActor.rnInterfaceIN^ieCoordinatorAdded()}
	
	/* Post Protocol:*/ 
	postP{ true}
	
	\end{lstlisting}
	\normalsize 
	
	
	
	





