\subsection{Operation Model for oeSendNewRequest}

\label{OM-oeSendNewRequest}


The \msrcode{oeSendNewRequest} operation has the following properties:

	\begin{operationmodel}
	\addheading{Operation}
	\adddoublerow{oeSendNewRequest}{sent to add a new request to the system’s post state.}

	\addrowheading{Parameters}
	\addnumbereddoublerow{}{APIName: dtName}{used to initialise the name field} 
	\addnumbereddoublerow{}{APICategory: etCategory}{used to initialise the category field} 
	\addnumbereddoublerow{}{APICity: dtCity}{used to initialise the city field} 

	\addrowheading{Return type}
	\addsinglerow{ptBoolean}

	\addrowheading{Pre-Condition (protocol)}
	\addnumberedsinglerow{PreP}{the system is started.
	the actor logged previously and did not log out!}
		
	\addrowheading{Pre-Condition (functional)}
	\addnumberedsinglerow{PreF}{it is supposed that there does NOT exists one ctRequest instance with the same name, category and city attributes than the one the person wants to add a new request.
	it is supposed that there does NOT exists one ctPI instance with the same name, category and city attributes than the one the person wants to add a new request.}

	\addrowheading{Post-Condition (functional)}
	\addnumberedsinglerow{PostF}{the new requested PI is added in the system's post state.
	the person actor is informed about the satisfaction of its request.}

	\addrowheading{Post-Condition (protocol)}
	\addnumberedsinglerow{PostP}{none}
	\end{operationmodel}



	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{OM-actPerson-oeSendNewRequest-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the operation.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the operation \emph{oeSendNewRequest}.},label=OM-actPerson-oeSendNewRequest-MCL-LST]

	/* Pre Protocol:*/ 
	preP{let TheSystem:ctState in
					let TheActor:actPerson in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = TheActor
					
					/* PreP01 */
					TheSystem.vpStarted = true
					
					/* PreP02 */
					and TheActor.rnctAuthenticated.vpIsLogged = true}
	
	/* Pre Functional:*/
	preF{let TheSystem:ctState in
					let TheActor:actPerson in
					let ColctPI:Set(ctPI) in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = TheActor
					
					/* PreF01 */
					TheSystem.rnctPI->select(name.eq(APIName) category.eq(APICategory) city.eq(APICity)) = ColctPI
					and ColctPI->IsEmpty() = true
					
					/* PreF02 */
					and TheSystem.rnctRequest->select(name.eq(APIName) category.eq(APICategory) city.eq(APICity)) = ColctRequest
					and ColctRequest->IsEmpty() = true}
	
	/* Post Functional:*/ 
	postF{let TheSystem:ctState in
					let TheActor:actPerson in
					let ThectRequest:ctRequest in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = TheActor
					
					/* PostF01 */
					ThectRequest.init(APIName, APICategory, APICity)
					
					/* PostF02 */
					and AMessage.eq('Request sent!')
					and TheActor.rnInterfaceIN^ieMessage(AMessage)}
	
	/* Post Protocol:*/ 
	postP{ true}
	
	\end{lstlisting}
	\normalsize 
	
	
	
	





