\subsection{Operation Model for oeAddPI}

\label{OM-oeAddPI}


The \msrcode{oeAddPI} operation has the following properties:

	\begin{operationmodel}
	\addheading{Operation}
	\adddoublerow{oeAddPI}{sent to add a new point of interest in the system’s post state.}

	\addrowheading{Parameters}
	\addnumbereddoublerow{}{APIID: dtID}{used to initialise the id field} 
	\addnumbereddoublerow{}{APIName: dtName}{used to initialise the name field} 
	\addnumbereddoublerow{}{APICity: dtCity}{used to initialise the city field} 
	\addnumbereddoublerow{}{APIGPSLocation: dtGPSLocation}{used to initialise the gps location field} 
	\addnumbereddoublerow{}{APIDescription: dtDescription}{used to initialise the description field} 
	\addnumbereddoublerow{}{APICategory: etCategory}{used to initialise the category field} 

	\addrowheading{Return type}
	\addsinglerow{ptBoolean}

	\addrowheading{Pre-Condition (protocol)}
	\addnumberedsinglerow{PreP}{the system is started.
	the actor logged previously and did not log out!}
		
	\addrowheading{Pre-Condition (functional)}
	\addnumberedsinglerow{PreF}{it is supposed that there exist one ctRequest instance with the same id attribute than the one the administrator wants to create.
	it is supposed that there does NOT exist one ctPI instance with the same id attribute than the one the administrator wants to create.}

	\addrowheading{Post-Condition (functional)}
	\addnumberedsinglerow{PostF}{the new PI is added to the system.
	the administrator actor is informed about the satisfaction of its request.
	the person actor is informed about the satisfaction of its request.}

	\addrowheading{Post-Condition (protocol)}
	\addnumberedsinglerow{PostP}{none}
	\end{operationmodel}



	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{OM-actAdministrator-oeAddPI-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the operation.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the operation \emph{oeAddPI}.},label=OM-actAdministrator-oeAddPI-MCL-LST]

	/* Pre Protocol:*/ 
	preP{let TheSystem:ctState in
					let TheActor:actAdministrator in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = TheActor
					
					/* PreP01 */
					TheSystem.vpStarted = true
					
					/* PreP02 */
					and TheActor.rnctAuthenticated.vpIsLogged = true}
	
	/* Pre Functional:*/
	preF{let TheSystem:ctState in
					let TheActor:actAdministrator in
					let ColctPI:Set(ctPI) in
					let ColctRequest:Set(ctRequest) in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = TheActor
					
					/* PreF01 */
					TheSystem.rnctPI->select(id.eq(APIID)) = ColctPI
					and ColctPI->IsEmpty() = true
					
					/* PreF02 */
					and TheSystem.rnctRequest->select(id.eq(APIID) status.eq("solved")) = ColctRequest
					and ColctRequest->IsEmpty() = false}
	
	/* Post Functional:*/ 
	postF{let TheSystem:ctState in
					let TheActor:actAdministrator in
					let ThectPI:ctPI in
					let ThePerson:actPerson in
					
					self.rnActor.rnSystem = TheSystem
					and self.rnActor = TheActor
					
					/* PostF01 */
					ThectPI.init(APIID, APIName, APICity, APIGPSLocation, APIDescription, APICategory)
					
					/* PostF02 */
					and TheActor.rnInterfaceIN^iePIAdded()
					
					/* PostF03 */
					and ThePerson.rnInterfaceIN^iePIAdded()}
	
	/* Post Protocol:*/ 
	postP{ true}
	
	\end{lstlisting}
	\normalsize 
	
	
	
	





